---
title: " "
author: ""
date: "4-Sept-2019. ADEH, Porto, Portugal"
output: 
  ioslides_presentation:
    css: styles.css
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r, echo = FALSE, include = FALSE, cache = TRUE,results = 'hide', message = FALSE, warning = FALSE}
library(here)
source(here("BirthFlows","R","Functions.R"))
source(here("BirthFlows","R","Method13_deBeer1985and1989-swe.R"))
source(here("BirthFlows","R","DataPrep_old.R"))
```

## The Swedish birth series

```{r, echo = FALSE, results = 'hide',fig.width=9,fig.height=4,fig.align='center'}
Bt2  <- Bt[Yrs <= 2017]
Yrs2 <- 1736:2017
Yrs3 <- 2017:2032
Bt3  <- Bt[Yrs %in% Yrs3]

par(xaxs="i",yaxs="i",mai=c(0,1,0,.2))
plot(Cohs, Bc, ylim = c(-250000,250000), xlim= c(1687,2090),type = 'n',
     axes=FALSE,ann=FALSE)
#polygon(c(min(Cohs),Cohs,max(Cohs)), c(0,Bc,0),col="#000000DF")
polygon(c(min(Yrs2),Yrs2,max(Yrs2)), c(0,Bt2,0),col="#000000")
abline(v=c(1800,1900,2000), col = "#FFFFFF80")
abline(h=c(50000,100000,150000),lwd=1,col="#FFFFFF80")
axis(2, las = 1, 
     at =c(150000,100000,50000,0),
     labels = c("150k","100k","50k",""))
axis(1, at= c(1736,1800,1900,2000), pos = 0)
```

## The Swedish birth series

```{r, echo = FALSE, results = 'hide',fig.width=9,fig.height=4,fig.align='center'}
par(xaxs="i",yaxs="i",mai=c(0,1,0,.2))
plot(Cohs, Bc, ylim = c(-250000,250000), xlim= c(1687,2090),type = 'n',
     axes=FALSE,ann=FALSE)
#polygon(c(min(Cohs),Cohs,max(Cohs)), c(0,Bc,0),col="#000000DF")
polygon(c(min(Yrs3),Yrs3,max(Yrs3)), c(0,Bt3,0),col="#000000BB")
polygon(c(min(Yrs2),Yrs2,max(Yrs2)), c(0,Bt2,0),col="#000000")
abline(h=c(50000,100000,150000),lwd=1,col="#FFFFFF80")
abline(v=c(1800,1900,2000), col = "#FFFFFF80")
axis(1, at= c(1736,1800,1900,2000, 2032), pos = 0)
axis(2, las = 1, 
     at =c(150000,100000,50000,0),
     labels = c("150k","100k","50k",""))
```

## The Swedish birth series

```{r, echo = FALSE, results = 'hide',fig.width=9,fig.height=4,fig.align='center'}
Cohs2 <- (1736-15):2016
Bc2   <- Bc[Cohs %in% Cohs2]
par(xaxs="i",yaxs="i",mai=c(0,1,0,.2))
plot(Cohs, Bc, ylim = c(-250000,250000), xlim= c(1687,2090),type = 'n',
     axes=FALSE,ann=FALSE)
polygon(c(min(Cohs2),Cohs2,max(Cohs2)), c(0,-Bc2,0),col="#000000AA")
polygon(c(min(Yrs3),Yrs3,max(Yrs3)), c(0,Bt3,0),col="#000000BB")
polygon(c(min(Yrs2),Yrs2,max(Yrs2)), c(0,Bt2,0),col="#000000")
abline(h=c(-50000,-100000,-150000,0,50000,100000,150000),lwd=1,col="#FFFFFF80")
abline(v=c(1736,1800,1900,2000), col = "#FFFFFF80")
axis(1, at= c(1721,1736,1800,1900,2000,2032), 
     labels = FALSE,
     pos = -160000)
text(c(1711,1736,1800,1900,2000,2032),-160000, c(1721,1736,1800,1900,2000,2032),pos=1, offset = 1.3)
axis(2, las = 1, 
     at =c(-150000,-100000,-50000,150000,100000,50000,0),
     labels = c("150k","100k","50k","150k","100k","50k",""))
```

## The Swedish birth series

```{r, echo = FALSE, results = 'hide',fig.width=9,fig.height=4,fig.align='center'}
Cohs2 <- (1736-15):2016
Bc2   <- Bc[Cohs %in% Cohs2]
par(xaxs="i",yaxs="i",mai=c(0,1,0,.2))
plot(Cohs, Bc, ylim = c(-250000,250000), xlim= c(1687,2090),type = 'n',
     axes=FALSE,ann=FALSE)
polygon(c(min(Cohs2),Cohs2,max(Cohs2)), c(0,-Bc2,0),col="#000000AA")
polygon(c(min(Yrs3),Yrs3,max(Yrs3)), c(0,Bt3,0),col="#000000BB")
polygon(c(min(Yrs2),Yrs2,max(Yrs2)), c(0,Bt2,0),col="#000000")
abline(h=c(-50000,-100000,-150000,0,50000,100000,150000),lwd=1,col="#FFFFFF80")
abline(v=c(1736,1800,1900,2000), col = "#FFFFFF80")
axis(1, at= c(1721,1736,1800,1900,2000,2032), 
     labels = FALSE,
     pos = -160000)
text(c(1711,1736,1800,1900,2000,2032),-160000, c(1721,1736,1800,1900,2000,2032),pos=1, offset = 1.3)
axis(2, las = 1, 
     at =c(-150000,-100000,-50000,150000,100000,50000,0),
     labels = c("150k","100k","50k","150k","100k","50k",""))
text(1900, 50000, "Births / year", cex = 2, col = "#FFFFFF")
text(1900, -50000, "The children they had", cex = 2, col = "#FFFFFF")
```

## We're 3/4 through the title! {.build}

- Boom  
- Echo
- Pulse
- <p style="color:red;">Flow</p>

## Structure reveals flow

```{r, echo = FALSE, results = 'hide',fig.width=9,fig.height=4,fig.align='center', message = FALSE, warning=FALSE}
library(tidyverse)
refyr     <- 1900
SWE       <- filter(SWE, ARDY >= 15 & ARDY <= 54)
BornIn    <- filter(SWE,Year == refyr)
BabiesHad <- filter(SWE,Cohort == refyr)
par(xaxs="i",yaxs = "i", mai = c(.5,1,.5,0))
plot(BornIn$ARDY, BornIn$Total, type = 'n',xlab = "Mother's age", ylab = "Count",axes=FALSE,ylim=c(0,7000), xlim = c(15,120))
draw_block_poly_grid(BornIn$ARDY, BornIn$Total, border = NA, col = gray(.3))
axis(2,las=1)
text(seq(15,50,by=5),0,seq(15,50,by=5),pos=1,xpd=TRUE)
```

## Structure reveals flow

```{r,fig.width=9,fig.height=4,fig.align='center', message = FALSE, warning=FALSE}
par(xaxs="i",yaxs = "i", mai = c(.5,1,.5,0))
plot(BornIn$Cohort, BornIn$Total, type = 'n',xlab = "Mother's Year of birth", ylab = "Count",axes=FALSE,ylim=c(0,7000), xlim = c(1850,1955))
draw_block_poly_grid(BornIn$Cohort, BornIn$Total, border = NA, col = gray(.3))
axis(2,las=1)
text(seq(1850,1885,by=10),0,seq(1850,1885,by=10),pos=1,xpd=TRUE)
```

## Structure reveals flow

```{r,fig.width=9,fig.height=4,fig.align='left', message = FALSE, warning=FALSE}
par(xaxs="i",yaxs = "i", mai = c(.5,1,.5,0))
plot(BornIn$Cohort, BornIn$Total, type = 'n',xlab = "Mother's Year of birth", ylab = "Count",axes=FALSE,ylim=c(0,7000), xlim = c(1850,1955))
draw_block_poly_grid(BornIn$Cohort, BornIn$Total, border = NA, col = gray(.3))
axis(2,las=1)
text(seq(1850,1940,by=10),0,seq(1850,1940,by=10),pos=1,xpd=TRUE)
draw_block_poly_grid(BabiesHad$Year, BabiesHad$Total, border = NA, col = gray(.3))
axis(2,las=1)
segments(seq(1890,1915,by=5),0,seq(1890,1915,by=5),100)
```


## Structure reveals flow

```{r,fig.width=9,fig.height=4,fig.align='left', message = FALSE, warning=FALSE}
par(xaxs="i",yaxs = "i", mai = c(.5,1,.5,0))
plot(BornIn$Cohort, BornIn$Total, type = 'n',xlab = "Mother's Year of birth", ylab = "Count",axes=FALSE,ylim=c(0,7000), xlim = c(1850,1955))
draw_block_poly_grid(BornIn$Cohort, BornIn$Total, border = NA, col = gray(.3))
axis(2,las=1)
text(seq(1850,1940,by=10),0,seq(1850,1940,by=10),pos=1,xpd=TRUE)
draw_block_poly_grid(BabiesHad$Year, BabiesHad$Total, border = NA, col = gray(.3))
axis(2,las=1)
segments(seq(1890,1915,by=5),0,seq(1890,1915,by=5),100)
segments(1900,0,1900,5000,col="red")
text(1900,5500,"1900 cohort link",cex=2)
```

## Structure reveals flow
```{r, echo = FALSE, results = 'hide',fig.width=9,fig.height=4,fig.align='center',message = FALSE, warning=FALSE}
library(here)
library(reshape2)
library(viridis)
SWE <- readRDS(here("BirthFlows","Data","SWE_final_old.rds"))

PC <- acast(SWE, Year ~ Cohort, value.var = "Total")
PC[is.na(PC)] <- 0
PC5 <- apply(PC,1,function(x, Cohs){
	groupN(x, Cohs, 5)
}, Cohs = Cohs)

# single cohort bin, 5-year calendar bins
P5C <- apply(PC,2,function(x, Yrs){
	groupN(x, Yrs, 5)
}, Yrs = Yrs)

PC5cs <- apply(PC5,2,cumsum)
P5Ccs <- apply(P5C,2,cumsum)
PC5cs <- rbind(0,PC5cs)
P5Ccs <- rbind(0,P5Ccs)

cohNA          <- Cohs < 1720 
perNA          <- Yrs > 2032
Coh_SD         <- apply(PC, 2, wsd, x = Yrs + .5)
Coh_SD[cohNA]  <- NA
Per_SD         <- apply(PC, 1, wsd, x = Cohs + .5)
Per_SD[perNA]  <- NA
Per_SD5   <- groupN(Per_SD, y = Yrs, n = 5, fun = mean)
Coh_SD5   <- groupN(Coh_SD, y = Cohs, n = 5, fun = mean)

breaks     <- pretty(c(Per_SD5,Coh_SD5),35)
fillcolors <- viridis(length(breaks) - 1, option = "A")

ColsC5               <- as.character(cut(Per_SD5, breaks = breaks, labels = fillcolors))
ColsP5               <- as.character(cut(Coh_SD5, breaks = breaks, labels = fillcolors))
ColsP5[is.na(ColsP5)] <- gray(.8)
ColsC5[is.na(ColsC5)] <- gray(.8)
Yrs5 <- unique(Yrs - Yrs %% 5)
Cohs5 <- unique(Cohs - Cohs %% 5)

par(xaxs="i",yaxs="i",mai=c(0,1,0,.2))
plot(Cohs, Bc, ylim = c(-250000,250000), xlim= c(1687,2090),type = 'n',
     axes=FALSE,ann=FALSE)
polygon(c(min(Cohs),Cohs,max(Cohs)), c(0,-Bc,0),col="#000000AA")
polygon(c(min(Yrs),Yrs,max(Yrs)), c(0,Bt,0),col="#000000")
#  for (i in 1:(nrow(PC5cs) - 1)){
#  	polygon(c(Yrs, rev(Yrs)), 
#  			c(PC5cs[i, ], rev(PC5cs[i + 1, ])), 
#  			col = ColsC5[i], 
#  			border = "#FFFFFF80", 
#  			lwd = .5)
#  }
# # # bottom
#  for (i in 1:(nrow(P5Ccs) - 1)){
#  	polygon(c(Cohs, rev(Cohs)), 
#  			-c(P5Ccs[i, ], rev(P5Ccs[i + 1, ])), 
#  			col = ColsP5[i], 
#  			border = "#FFFFFF80", 
#  			lwd = .5)
#  	
#  }
axis(2,las=1,at =c(150000,100000,50000,0,-50000,-100000,-150000), 
		labels=c("150k","100k","50k","","50k","100k","150k"))
axis(1,at=seq(1700,2050,by=50),pos=-160000)

polygon(c(1900:1905, 1905:1900),c(Bt[Yrs%in%c(1900:1905)],rep(0,6)),
        col = ColsC5[Yrs5==1895])
polygon(c(1900:1905, 1905:1900),-c(Bc[Cohs%in%c(1900:1905)],rep(0,6)),
        col = ColsP5[Cohs5==1900])

# highlight 1900
Yrs5 <- unique(Yrs - Yrs %% 5)
Cohs5 <- unique(Cohs - Cohs %% 5)
# polygon(c(Yrs, rev(Yrs)), 
# 			c(PC5cs["1900", ], rev(PC5cs["1905", ])), 
# 			col = ColsP5[Yrs5==1900], 
# 			border = "#000000DD", 
# 			lwd = .5)
# polygon(c(Cohs, rev(Cohs)), 
# 			-c(P5Ccs["1900", ], rev(P5Ccs["1905", ])), 
# 			col = ColsC5[Cohs5==1900], 
# 			border = "#000000DD", 
# 			lwd = .5)
		
```

## Structure reveals flow
```{r, echo = FALSE, results = 'hide',fig.width=9,fig.height=4,fig.align='center',message = FALSE, warning=FALSE}

par(xaxs="i",yaxs="i",mai=c(0,1,0,.2))
plot(Cohs, Bc, ylim = c(-250000,250000), xlim= c(1687,2090),type = 'n',
     axes=FALSE,ann=FALSE)
polygon(c(min(Cohs),Cohs,max(Cohs)), c(0,-Bc,0),col="#000000AA")
polygon(c(min(Yrs),Yrs,max(Yrs)), c(0,Bt,0),col="#000000")
  for (i in 1:(nrow(PC5cs) - 1)){
  	polygon(c(Yrs, rev(Yrs)), 
  			c(PC5cs[i, ], rev(PC5cs[i + 1, ])), 
  			col = NA, 
  			border = "#FFFFFF80", 
  			lwd = .5)
  }
 # # bottom
  for (i in 1:(nrow(P5Ccs) - 1)){
  	polygon(c(Cohs, rev(Cohs)), 
  			-c(P5Ccs[i, ], rev(P5Ccs[i + 1, ])), 
  			col = NA, 
  			border = "#FFFFFF80", 
  			lwd = .5)
  	
  }
axis(2,las=1,at =c(150000,100000,50000,0,-50000,-100000,-150000), 
		labels=c("150k","100k","50k","","50k","100k","150k"))
axis(1,at=seq(1700,2050,by=50),pos=-160000)

polygon(c(1900:1905, 1905:1900),c(Bt[Yrs%in%c(1900:1905)],rep(0,6)),
        col = ColsC5[Yrs5==1895])
polygon(c(1900:1905, 1905:1900),-c(Bc[Cohs%in%c(1900:1905)],rep(0,6)),
        col = ColsP5[Cohs5==1900])
# highlight 1900
Yrs5 <- unique(Yrs - Yrs %% 5)
Cohs5 <- unique(Cohs - Cohs %% 5)
# polygon(c(Yrs, rev(Yrs)), 
# 			c(PC5cs["1900", ], rev(PC5cs["1905", ])), 
# 			col = ColsP5[Yrs5==1900], 
# 			border = "#000000DD", 
# 			lwd = .5)
# polygon(c(Cohs, rev(Cohs)), 
# 			-c(P5Ccs["1900", ], rev(P5Ccs["1905", ])), 
# 			col = ColsC5[Cohs5==1900], 
# 			border = "#000000DD", 
# 			lwd = .5)
```

## Structure reveals flow
```{r, echo = FALSE, results = 'hide',fig.width=9,fig.height=4,fig.align='center',message = FALSE, warning=FALSE}

par(xaxs="i",yaxs="i",mai=c(0,1,0,.2))
plot(Cohs, Bc, ylim = c(-250000,250000), xlim= c(1687,2090),type = 'n',
     axes=FALSE,ann=FALSE)
polygon(c(min(Cohs),Cohs,max(Cohs)), c(0,-Bc,0),col="#000000AA")
polygon(c(min(Yrs),Yrs,max(Yrs)), c(0,Bt,0),col="#000000")
  for (i in 1:(nrow(PC5cs) - 1)){
  	polygon(c(Yrs, rev(Yrs)), 
  			c(PC5cs[i, ], rev(PC5cs[i + 1, ])), 
  			col = NA, 
  			border = "#FFFFFF80", 
  			lwd = .5)
  }
 # # bottom
  for (i in 1:(nrow(P5Ccs) - 1)){
  	polygon(c(Cohs, rev(Cohs)), 
  			-c(P5Ccs[i, ], rev(P5Ccs[i + 1, ])), 
  			col = NA, 
  			border = "#FFFFFF80", 
  			lwd = .5)
  	
  }
axis(2,las=1,at =c(150000,100000,50000,0,-50000,-100000,-150000), 
		labels=c("150k","100k","50k","","50k","100k","150k"))
axis(1,at=seq(1700,2050,by=50),pos=-160000)
  
polygon(c(1900:1905, 1905:1900),c(Bt[Yrs%in%c(1900:1905)],rep(0,6)),
        col = ColsC5[Yrs5==1895])
polygon(c(1900:1905, 1905:1900),-c(Bc[Cohs%in%c(1900:1905)],rep(0,6)),
        col = ColsP5[Cohs5==1900])

# highlight 1900
Yrs5 <- unique(Yrs - Yrs %% 5)
Cohs5 <- unique(Cohs - Cohs %% 5)
 polygon(c(Yrs, rev(Yrs)), 
 			c(PC5cs["1900", ], rev(PC5cs["1905", ])), 
 			col = ColsP5[Cohs5==1900], 
 			border = "#000000DD", 
 			lwd = .5)
 polygon(c(Cohs, rev(Cohs)), 
 			-c(P5Ccs["1900", ], rev(P5Ccs["1905", ])), 
 			col = ColsC5[Yrs5==1895], # not sure why had to shift
 			border = "#000000DD", 
 			lwd = .5)
```

## Structure reveals flow
```{r, echo = FALSE, results = 'hide',fig.width=9,fig.height=4,fig.align='center',message = FALSE, warning=FALSE}

par(xaxs="i",yaxs="i",mai=c(0,1,0,.2))
plot(Cohs, Bc, ylim = c(-250000,250000), xlim= c(1687,2090),type = 'n',
     axes=FALSE,ann=FALSE)
polygon(c(min(Cohs),Cohs,max(Cohs)), c(0,-Bc,0),col="#000000AA")
polygon(c(min(Yrs),Yrs,max(Yrs)), c(0,Bt,0),col="#000000")
  for (i in 1:(nrow(PC5cs) - 1)){
  	polygon(c(Yrs, rev(Yrs)), 
  			c(PC5cs[i, ], rev(PC5cs[i + 1, ])), 
  			col = ColsP5[i], 
  			border = "#FFFFFF80", 
  			lwd = .5)
  }
 # # bottom
  for (i in 1:(nrow(P5Ccs) - 1)){
  	polygon(c(Cohs, rev(Cohs)), 
  			-c(P5Ccs[i, ], rev(P5Ccs[i + 1, ])), 
  			col = ColsC5[i], 
  			border = "#FFFFFF80", 
  			lwd = .5)
  }
axis(2,las=1,at =c(150000,100000,50000,0,-50000,-100000,-150000), 
		labels=c("150k","100k","50k","","50k","100k","150k"))
axis(1,at=seq(1700,2050,by=50),pos=-160000)
```

## Structure reveals flow

```{r, echo = FALSE, results = 'hide',fig.width=9,fig.height=4,fig.align='center',message = FALSE, warning=FALSE}

par(xaxs="i",yaxs="i",mai=c(0,1,0,.2))
plot(Cohs, Bc, ylim = c(-250000,250000), xlim= c(1687,2090),type = 'n',
     axes=FALSE,ann=FALSE)
polygon(c(min(Cohs),Cohs,max(Cohs)), c(0,-Bc,0),col="#000000AA")
polygon(c(min(Yrs),Yrs,max(Yrs)), c(0,Bt,0),col="#000000")
  for (i in 1:(nrow(PC5cs) - 1)){
  	polygon(c(Yrs, rev(Yrs)), 
  			c(PC5cs[i, ], rev(PC5cs[i + 1, ])), 
  			col = ColsP5[i], 
  			border = "#FFFFFF80", 
  			lwd = .5)
  }
 # # bottom
  for (i in 1:(nrow(P5Ccs) - 1)){
  	polygon(c(Cohs, rev(Cohs)), 
  			-c(P5Ccs[i, ], rev(P5Ccs[i + 1, ])), 
  			col = ColsC5[i], 
  			border = "#FFFFFF80", 
  			lwd = .5)
  }
axis(2,las=1,at =c(150000,100000,50000,0,-50000,-100000,-150000), 
		labels=c("150k","100k","50k","","50k","100k","150k"))
axis(1,at=seq(1700,2050,by=50),pos=-160000)
text(1900, 50000, "Births / year", cex = 2, col = "#FFFFFF")
text(1900, -50000, "The children they had", cex = 2, col = "#FFFFFF")
```

## Check out the paper!


<img src = "wpqr.svg" >

(The poster is outside)

Thanks!

riffe@demogr.mpg.de